Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-27 6-ModelPresentation.tex
sync d'une version compilable
Updates from Overleaf

Ici: un paragraphe qui décrit l'exécution, l'activation et la finalisation des taches, la business logic des gateways, etc...

@@

The other tool, an \textit{enacted process editor}, provides process edition and tasks assignations through a graphical visualization displaying process being executed. This tool is represented one the right side of the figure \ref{fig:ToolingArchitecture}. It follows the same architecture pattern as explicited for the \textit{process type graphical editor}, with two model slots referencing both the model and a diagram. Process enactment is operated from a \textit{ProcessType}, and must be defined using a name identifying the newly instantiated process. All tasks are created from their \textit{TaskType} definition, and required assignments applies (if for example "Coding" \textit{TaskType} defines COBOL as output programming language, related task is automatically assigned to "Ann Smith"). All tasks get a status (\textit{Not startable} - when not assigned or when required input artifacts are not available - , \textit{Startable}, \textit{Started}, \textit{Completable}, \textit{Completed}), as well as a set of performing actors, a begin and end date, and used and produced artifacts. This tools also manages creation of artifacts, whose semantics follows rules defined in section \ref{sec:ProcessEnactment}}

>>>>

\todo[inline]{Ici: un paragraphe qui décrit l'exécution, l'activation et la finalisation des taches, la business logic des gateways, etc...}

@@

The other tool, an \textit{enacted process editor}, provides process edition and tasks assignations through a graphical visualization displaying process being executed. This tool is represented one the right side of the figure \ref{fig:ToolingArchitecture}. It follows the same architecture pattern as explicited for the \textit{process type graphical editor}, with two model slots referencing both the model and a diagram. Process enactment is operated from a \textit{ProcessType}, and must be defined using a name identifying the newly instantiated process. All tasks are created from their \textit{TaskType} definition, and required assignments applies (if for example "Coding" \textit{TaskType} defines COBOL as output programming language, related task is automatically assigned to "Ann Smith"). All tasks get a status (\textit{Not startable} - when not assigned or when required input artifacts are not available - , \textit{Startable}, \textit{Started}, \textit{Completable}, \textit{Completed}), as well as a set of performing actors, a begin and end date, and used and produced artifacts. This tool also manages creation of artifacts, whose semantics follows rules defined in section \ref{sec:ProcessEnactment} (\textbf{P13}).
